Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-07-26 writing/embedded_meta_learning_main.tex
Further tweaking

This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1. We could then evaluate whether the system loses with this $\hat{z}_{new}$ strategy. This is how we evaluate meta-mapping performance -- evaluating the loss on the target task after transforming the task embedding. \par

@@

\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in fig. \ref{poly_meta_map_results}. We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial. We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on. The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping or receiving a natural-language instruction. It performs slightly better from examples than language, since examples provide a richer description of the meta-mapping. \par 

@@

In order to adapt the EML architecture, we made a very simple change. Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state. (A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, we saw it as a useful proof of concept.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues. That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game. We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose. Details of the architecture and training can be found in appendix \ref{app_detailed_methods}. \par

>>>>

This $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for game 1. To train a meta-mapping, we minimize the $\ell_2$ loss in the latent space betwen this guess and the embedding of the losing task. Whether or not we have such a target embedding, we can evaluate how well the system loses with this $\hat{z}_{new}$ strategy. This is how we evaluate meta-mapping performance -- evaluating the loss on the target task after transforming the task embedding. \par

@@

\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior, as shown in fig. \ref{poly_meta_map_results}. We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial. We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on. The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping or receiving a natural-language cue to the meta-mapping. It performs slightly better from examples than language, since examples provide a richer description of the meta-mapping. \par 

@@

In order to adapt the EML architecture, we made a very simple change. Instead of providing the system with (input, target) tuples to embed, we provided it with (state, action, reward) tuples, and trained it via a DQN-like approach \citep{Mnih2015} to predict rewards for each bet in each state. (A full RL framework is not strictly necessary here because there is no temporal aspect to the tasks; however, because the outcome is only observed for the action you take, it is not a standard supervised task.) The hand is explicitly provided to the network for each example, but which game is being played is implicitly captured in the training examples, without any explicit cues. That is, the system must learn to play directly from seeing a set of (state, action, reward) tuples which implicitly capture the structure and stochasticity of the game. We also trained the system on meta-tasks, such as to identifying the various types of games and options, and to make meta-mappings, for example switching from trying to win a game to trying to lose. Details of the architecture and training can be found in appendix \ref{app_detailed_methods}. \par

### 2019-07-26 writing/nips_submission/response/EML_response.tex
Further tweaking

\textbf{miniImageNet:} \par

@@

\textbf{Novelty and contributions:} As all three reviewers noted, the most novel contribution of our paper is the proposal to thing about transfer in terms of meta-mappings and task transformations. The architecture we propose is designed with this idea in mind. It is true that previous work has considered task embeddings (some of the works suggested by the reviewers we have mentioned in the related works section, but some we were not familiar with, we appreciate the pointers). Most of these have developed some way of embedding a dataset into some latent space. However, what we think is fundamentally novel about our architecture is that \textbf{we use the same latent space for the dataset as we use for an individual input to the network}. This allows us to use the same meta and hyper networks for both basic tasks and meta-mappings, which we show in appendix D.1 performs better than separate embedding spaces for basic inputs and tasks. We think that this is a fundamentally novel aspect of our architecture, since it is primarily useful for the types of tasks we propose. While other techniques that create explicit task embeddings could also be trained to transform them for meta-mappings, we think our novel insight of a shared embedding space for individual data points and tasks would result in better performance in these domains too. We do think that combining other meta-learning approaches such as MAML with a system like ours is an interesting direction for future work. As we point out in the future directions, we do not expect the exact approach we've proposed to be the best way of solving these problems. However, it does provide a useful starting point. We think that the primary contribution of this work is highlighting the idea of meta-mappings for transfer, and providing some starting points for how to approach them by taking a functional perspective, which we hope will inspire future work. \par

@@

\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary. We explored some variations in appendix D to justify a few hoices, and showed that some more parsimonious choices resulted in worse performance. However, we acknowledge that we have not explored the full space of models or algorithms which could be used to approach this problem, and we see this as an important direction for future work. This problem is not exactly a standard supervised problem because you predict rewards for several actions, but only observe the reward for the action you execute, but we are not using a full DQN. We have revised the manuscript to clarify this point. \par 

@@

\textbf{Natural language:} was simply used as a meta-mapping cue in the main text. Specifically, we used the language embedding as input to the hyper network to generate the meta-mapping parameters. In appendix A we compare to specifying new tasks directly from language. Meta-mappings perform better, presumably by leveraging task knowledge. \par

@@

\textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work use this. We think the memory requirements of this approach compare favorably to many other approaches for continual learning, since it only requires storing an embedding vector per task, whereas many approaches (such as EWC) require storing an extra ``importance'' parameter for each parameter in the model. For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume even up to hundreds of thousands of tasks. We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it. \par

>>>>

\textbf{miniImageNet:} TBD. \par

@@

\textbf{Novelty and contributions:} As all three reviewers noted, the most novel contribution of our paper is the proposal to thing about transfer in terms of meta-mappings and task transformations. The architecture we propose is designed with this idea in mind. It is true that previous work has considered task embeddings (some of the works suggested by the reviewers we have mentioned in the related works section, but some we were not familiar with, we appreciate the pointers). Most of these have developed some way of embedding a dataset into some latent space. However, what we think is fundamentally novel about our architecture is that \textbf{we use the same latent space for the dataset as we use for an individual input to the network}. This allows us to use the same meta and hyper networks for both basic tasks and meta-mappings, which we show in appendix D.1 performs better than separate embedding spaces. We think that this is a fundamentally novel aspect of our architecture, since it is primarily useful for the types of tasks we propose. While other techniques that create explicit task embeddings could also be trained to transform them for meta-mappings, we think our novel insight of a shared embedding space for individual data points and tasks would result in better performance in these domains too. We do think that combining other meta-learning approaches such as MAML with a system like ours is an interesting direction for future work. As we point out in the future directions, we do not expect the exact approach we've proposed to be the best way of solving these problems. However, it does provide a useful starting point. We think that the primary contribution of this work is highlighting the idea of meta-mappings for transfer, and providing some starting points for how to approach them by taking a functional perspective, which we hope will inspire future work. \par

@@

\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary. We explored some variations in appendix D to justify a few hoices, and showed that some more parsimonious choices resulted in worse performance. However, we acknowledge that we have not explored the full space of models or algorithms which could be used to approach this problem, and we see this as an important direction for future work. The problem as we have defined it is not exactly a standard supervised problem because you only observe the reward for the action you execute, but we are not using a full DQN. We have revised the manuscript to clarify these points. \par 

@@

\textbf{Natural language:} Language was simply used as a meta-mapping cue in the main text. Specifically, we used the language embedding as input to the hyper network to generate the meta-mapping parameters. In appendix A we compare to specifying new tasks directly from language. Meta-mapping works better, presumably by better using task knowledge. \par

@@

\textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work suggest this. We think the memory requirements of this approach compare favorably to many other approaches for continual learning, since it only requires storing an embedding vector per task, whereas many approaches (such as EWC) require storing an extra ``importance'' parameter for each parameter in the model. For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume less memory than doubling the parameter count, even up to millions of tasks. We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it in the text. \par
